### 2015-05-13 corral.tex
update in corral section to talk about pairs

>>>>

In this work, we use \corral to analyze separate pairs of entry points (as outputted by \whoop), instead of the whole Boogie driver (as outputted by SMACK). We also do not employ any abstraction to model additional threads, as we want \corral to report only true races. Because we only analyze pairs, though, \corral can miss races that require more than two threads to manifest. We argue that this limitation is orthogonal to this work: as long as we compare the same pairs with standalone \corral and with \corral that takes advantage of \whoop, then our comparison is sound. In reality, we could allow \corral to analyze the whole driver, and then instrument \texttt{yield} statements in a coarser granularity (taking into account all threads).

### 2015-05-13 evaluation.tex
update in corral section to talk about pairs

\noindent
\textbf{Experimental Setup}\xspace\xspace We performed all experiments on a 3.40GHz Intel Core i7-2600 CPU with 16GB RAM running Ubuntu Linux 12.04.5 LTS, LLVM 3.5, SMACK 1.5, Z3 4.3.2, Boogie rev. 4192 and \corral rev. 534.  \ADComment{Perhaps also state that Boogie runs inside Mono, and give the Mono version?}

\noindent
\textbf{Benchmarks}\xspace\xspace We evaluate our methodology against \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel. We chose non-trivial drivers from several domains: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. We had to manually model the environment for these drivers, a process that required approximately two months of work.  \ADComment{Question from me: are block and char domains, in the same way that ethernet is a domain?}

@@

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analysing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false alarm race reports.  On the other hand, \corral is precise, but can miss races because only a limited number of context switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.  \ADComment{Would this be a good point to reiterate the fact that when we apply \corral to an entry point pair, we are just checking the specific pair of threads, and are not accounting for actions by other threads?}

>>>>

\noindent
\textbf{Experimental Setup}\xspace\xspace We performed all experiments on a 3.40GHz Intel Core i7-2600 CPU with 16GB RAM running Ubuntu Linux 12.04.5 LTS, LLVM 3.5, SMACK 1.5, Z3~4.3.2, Boogie rev. 4192 and \corral rev. 534. We also used Mono~4.1.0 to run Boogie and \corral.

\noindent
\textbf{Benchmarks}\xspace\xspace We evaluate our methodology against \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel. We chose non-trivial drivers from several categories: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. We had to manually model the environment for these drivers, a process that required approximately two months of work.

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analysing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false alarm race reports.  On the other hand, \corral is precise, but can miss races because only a limited number of context switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.

\ADComment{Would this be a good point to reiterate the fact that when we apply \corral to an entry point pair, we are just checking the specific pair of threads, and are not accounting for actions by other threads?}

@@
